### 2015-04-17 implementation-environment.tex
Fix typos.  Add gperftools section.
Module section

Spack's compiler wrappers have a number of useful effects.  First, they allow
Spack to transparently parameterize the compiler for most builds and for
Spack users to easily request a build with a new compiler swapped in.
Second, they enforce the use of {\tt RPATHs} in
installed binaries.  This causes applications built by Spack to run correctly
{\it regardless of the environment}.  Third, because compiler wrappers add 
header and library search paths for dependencies, header and library detection
tests run by most build systems succeed automatically, {\it without}
the need to use special arguments for nonstandard locations.  {\tt configure}
commands in Spack's {\tt install} function can have fewer arguments, and can
be written as they would be for system installs.  This reduces complexity
for package maintainers and enforces consistent, reproducible
build policies across packages.  Finally, because Spack has control over the 
wrappers, package authors can programmatically filter the compiler flags
used by software build systems, a useful last resort when porting to
bleeding-edge platforms or new, esoteric compilers.

\subsubsection{Environment Module Integration}
	\todo{.5 page}

TACC expects the user to run with the same
environment that she built with~\cite{mclay:lmod-tutorial}.

But, at LC, the user is
frequently not the builder of the application, and may not know the particular
incantation required to load the its environment. Moreover, users frequently run more 
than one application in the same job, each built by a separate team, and each with
its own environment. Most LC users are used to running programs with
specific paths; only 10\% use environment modules extensively.

@@

\begin{verbatim}
module disadvantages:
	- lmod solves a lot of problems
	- not on all systems
		- users often run from just a path.
		- not guaranteed that LD_LIBRARY_PATH, etc will
		  be set correctly.

- Lmod assumes build & submit environment must match
	- users often have NO IDEA what environment a package
	  was built with
	- multiple apps may be built with different stacks
	- combining them in a workflow is difficult with modules
		(need to know right incantation)

	- TACC implements a rather complicated mapping back to
	    the build env (Lmod CheckExec)

- Spack solves the matrix problem mentioned in the Lmod
    presentation (slide 98)
	- hierarchy is nasty -- every branch represents a
	  greedy choice
	- might NEED a specific version of ONE dependency
	  that is not supported in the tree
	  => SPACK!

- libmesh
	- boost, petsc, trilinos, grvy, etc.
\end{verbatim}

>>>>

Spack's compiler wrappers have a number of useful effects.  First, they allow
Spack to transparently parametrize the compiler for most builds and for
Spack users to easily request a build with a new compiler swapped in.
Second, they enforce the use of {\tt RPATHs} in
installed binaries.  This causes applications built by Spack to run correctly
{\it regardless of the environment}.  Third, because compiler wrappers add 
header and library search paths for dependencies, header and library detection
tests run by most build systems succeed automatically, {\it without}
the need to use special arguments for nonstandard locations.  {\tt configure}
commands in Spack's {\tt install} function can have fewer arguments, and can
be written as they would be for system installs.  This reduces complexity
for package maintainers and enforces consistent, reproducible
build policies across packages.  Finally, because Spack has control over the 
wrappers, package authors can programmatically filter the compiler flags
used by software build systems, a useful last resort when porting to
bleeding-edge platforms or new, esoteric compilers.

\subsubsection{Environment Module Integration}
\label{sec:envmodule}
In addition to build-time environments, Spack can also assist in create run-time
environments.  A package may need environment variables like {\tt PATH}, 
{\tt LD_LIBRARY_PATH}, or {\tt MANPATH} set before they can be used.  Some users
may prefer to manually point environment variables and paths at packages, and 
Section~\ref{sec:package-views} discusses how Spack can assist those users.  
As discussed in Section~\ref{sec:motivation}, many sites rely on environment 
modules to set their runtime environment.  Spack can automatically create 
dotkit~\cite{dotkit} and Module configuration files for its packages, allowing 
users to setup their runtime environment using familiar systems.

Future versions of Spack may also allow the creation of Lmod~\cite{mclay:lmod} 
module files.  Lmod allows users to load packages using a heirarchy of module 
load operations.  For example, a user might load a {\tt gcc} module and a 
{\tt mvapich2} module, and a subsequent load of the {\tt MPILeaks} package would 
load the appropriate version for that compiler and MPI implementation.  Spack 
understands where packages would fit in the Lmod hierarchy, allowing it to create 
Lmod module files.

@@

\end{verbatim}

### 2015-04-17 usecase-policy.tex
Module section

\todo{fill in citations below}
While Spack can easily create a dozen installs of a package like MPILeaks across different compilers and MPI implementations, it can be difficult for an end-user to determine which of those dozen packages should be used with their application.  The module (cite) or dotkit (cite) package managers are commonly used on supercomputer systems to solve this problem, and Spack allows the package administrator to automatically create module and dotkit files for packages Spack installs.

>>>>

While Spack can easily create a dozen installs of a package like MPILeaks across different compilers and MPI implementations, it can be difficult for an end-user to determine which of those dozen packages should be used with their application.  As discussed in Section~\ref{sec:envmodule}, environment modules are commonly used on supercomputer systems to solve this problem, and Spack allows the package administrator to automatically create module and dotkit files for packages Spack installs.
